\section{References}

[1] M. Alkhalaf, P. Yu, M. Yin, and C. Deng, "Applying generative AI with retrieval-augmented generation to summarize and extract key clinical information from electronic health records," Journal of Biomedical Informatics, p. 104662, 2024.

[2] T. Searle, Z. Ibrahim, J. Teo, and R. J. B. Dobson, "Discharge summary hospital course summarization of inpatient electronic health record text with clinical concept-guided deep pre-trained transformer models," Journal of Biomedical Informatics, p. 104358, 2023.

[3] S. Sai et al., "Generative AI for transformative healthcare: A comprehensive study of emerging models, applications, case studies, and limitations," IEEE Access, vol. 12, pp. 31078-31106, 2024.

[4] S. Reddy, "Generative AI in healthcare: An implementation science-informed translational path on application, integration, and governance," Implementation Science, vol. 19, p. 27, 2024.

[5] P. Zhang and M. N. Kamel Boulos, "Generative AI in medicine and healthcare: Promises, opportunities, and challenges," Future Internet, vol. 15, no. 9, p. 286, 2023.

[6] Leveraging generative AI models for synthetic data generation in healthcare: Balancing research and privacy, in 2023 International Conference on Smart Applications, Communications and Networking (SmartNets), 2023.

[7] W. Saba, S. Wendelken, and J. Shanahan, "Question-answering-based summarization of electronic health records using retrieval-augmented generation," arXiv preprint arXiv:2401.01469, 2024.

[8] Redefining medicine: The power of generative AI in modern healthcare, in 2024 5th International Conference on Smart Electronics and Communication (ICOSEC), 2024.

[9] D. S. W. Ting et al., "Retrieval-augmented generation for large language models and its generalizability in assessing medical fitness," arXiv preprint arXiv:2410.08431, 2024.

[10] L. M. Amugongo et al., "Retrieval-augmented generation for large language models in healthcare: A systematic review," Preprints, 2024.

[11] A. Bora and H. Cuayáhuitl, "Systematic analysis of retrieval-augmented generation-based LLMs for medical chatbot applications," Machine Learning and Knowledge Extraction, vol. 6, pp. 2355–2374, 2024.

[12] E. Albaroudi, T. Mansouri, and A. Alameer, "The intersection of generative AI and healthcare: Addressing challenges to enhance patient care," in 2024 Seventh International Women in Data Science Conference (WiDS PSU), 2024.

[13] Y. Xu, "The investigation of the application of RAG technology in the field of EHR," Science and Technology of Engineering, Chemistry and Environmental Protection, 2024.

[14] C. Troy, S. Sturley, J. M. Alcaraz-Calero, and Q. Wang, "Enabling generative AI to produce SQL statements: A framework for the auto-generation of knowledge based on EBNF context-free grammars," IEEE Access, vol. 11, pp. 123543-123564, 2023.

[15] P. Omrani et al., "Hybrid retrieval-augmented generation approach for LLMs query response enhancement," in 2024 10th International Conference on Web Research (ICWR), 2024.

[16] G. Papanastasiou, N. Dikaios, J. Huang, C. Wang, and G. Yang, "Is attention all you need in medical image analysis? A review," IEEE Journal of Biomedical and Health Informatics, vol. 28, no. 3, pp. 1398-1411, 2024. 